\documentclass[12pt]{article}
\usepackage{fullpage}

\newcommand{\appItem}[2] {
  \noindent{\bf #1:}
  #2 \\}

\begin{document}                            

\thispagestyle{empty}


\appItem{Team Name}{Jason Rohrer}

\appItem{Developer Names}{Jason Rohrer}

\appItem{Team Lead}{Jason Rohrer}

\appItem{Game Title}{Cultivation}

\appItem{Game Description}{Cultivation explores the social interactions within a gardening community.  You lead one family of gardeners, starting with a single individual, and wise choices can keep your genetic line from extinction.  While breeding plants, eating, and mating, your actions impact your neighbors, and the social balance sways between conflict and compromise.}

\appItem{System Requirements}{{\em Operating Systems:} Windows 95/98/2000/XP/etc., Mac OS X (tested on 10.2 for PPC), GNU/Linux.  {\em Required:} OpenGL, Mouse.  {\em Recommended:}  3D card that can render OpenGL, 400MHz processor, Stereo headphones.}

\appItem{Are you planning entering the Student Competition?}{No}

\appItem{Please list all pre-existing development engines and libraries, and all pre-existing art and audio assets used in your game}{OpenGL for cross-platform graphic rendering, PortAudio for cross-platform sound output.}

\appItem{Faculty Advisor Name}{Not applicable}

\appItem{Faculty Advisor Contact E-mail}{Not applicable}

\appItem{Link to Game}{http://cultivation.sf.net}

\appItem{Contact E-mail}{jcr13@users.sf.net}

\appItem{Contact Phone}{315-265-0585}

\appItem{Street Address}{93 Elm St.}

\appItem{City/State/Zip}{Potsdam, NY 13676}

\appItem{Country}{USA}

\appItem{Where did you hear about the Competition?}{I entered a game in the Slamdance 2005 BigC.  I don't remember how I heard about the BigC.}
\appItem{Would you like to receive Guerilla Gamemaker Competition e-mail updates?}{Yes}

\end{document}   
